Mixture Models for Single-Cell Assays with Application to Vaccine Studies: Supplementary Materials

### 2012-12-03 SupplementaryMaterialMIMOSA.tex
Revised for Biostatistics

\documentclass{article}
\title{Web-based Supplementary Materials for Mixture Models for Single-Cell Assays with Application to Vaccine Studies by Greg Finak, Andrew McDavid, Pratip Chattopadhyay, Maria Dominguez, Steve De Rosa, Mario Roederer and Raphael Gottardo}

\usepackage[margin=1in]{geometry}
\usepackage{amssymb}
\usepackage{booktabs}
\usepackage{multirow,natbib}
\usepackage{url}
\def\bSig\mathbf{\Sigma}
\newcommand{\VS}{V\&S}
\newcommand{\tr}{\mbox{tr}}
\usepackage{amsmath,tikz}
\usetikzlibrary{calc}
\usetikzlibrary{positioning}
\date{}
\begin{document}
\maketitle
\appendix
%\renewcommand{\thesection}{\Alph{section}}
\renewcommand{\thesubsection}{Web Appendix \Alph{subsection}:}
%\setcounter{section}{1}
\setcounter{subsection}{0}
%\setcounter{figure}{0}
\renewcommand{\figurename}{\textbf{Web Figure}}
\renewcommand{\thefigure}{\textbf{\Alph{figure}}}
\setcounter{figure}{0}
%\todo[inline]{Note that the Supplementary Information section needs corrections to notation and overall}

\section*{}
\subsection{Computational details for the beta-binomial model}
\noindent\textbf{Marginal likelihood derivations}\\
For a given subject $i$, the null marginal likelihood is obtained after integrating out the prior from the likelihood for model ${\cal M}_0$, as follows,
\[
\begin{split}
\mathrm{L_0}(\alpha_u,\beta_u|n_{si},n_{ui}) =&\int_0^1 \mathrm{Pr}(n_{si},n_{ui}|p_u)\pi(p_u|\alpha_u,\beta_u)\mathrm{d}p_u\\
=& \int_0^1Pr(n_s|p_u)Pr(n_u|p_u)\pi(p_u|\alpha_u,\beta_u) \mathrm{d}p_u\\
=&\int_0^1\binom{N_s}{n_s}p_u^{n_s}(1-p_u)^{N_s-n_s}\binom{N_u}{n_u}p_u^{n_u}(1-p_u)^{N_u-n_u}\frac{1}{\mathrm{B}(\alpha_u,\beta_u)}p_u^{\alpha_u-1}(1-p_u)^{\beta_u-1} \mathrm{d}p_u\\
=&\binom{N_s}{n_s}\binom{N_u}{n_u}\frac{1}{\mathrm{B}(\alpha_u,\beta_u)}\int_0^1 p_u^{n_s+n_u+\alpha_u-1}(1-p_u)^{N_s+N_u-n_s-n_u+\beta_u-1} \mathrm{d}p_u\\
=&\binom{N_s}{n_s}\binom{N_u}{n_u}\frac{\mathrm{B}(n_s+n_u+\alpha_u,N_s+N_u-n_s-n_u+\beta_0)}{\mathrm{B}(\alpha_u,\beta_u)}.
\end{split}
\]

\noindent\textbf{MCMC algorithm}\\
In what follows, we use $(x|y)$ to denote the conditional distribution of $x$ given $y$. In particular, we use $(x|\cdots)$ to denote the distribution of $x$ conditional on everything else in the model. Our MCMC algorithms cycles through the following steps: 
\begin{enumerate}
\item Update each $\alpha_u, \beta_u, \alpha_s$ and $\beta_s$ by Metropolis-Hastings using a Gaussian symmetric proposal where the variance of the proposal is tuned for each parameter using the approach of~\cite{Gelman:2004tc}.
\item Update $w$ by Gibbs sampling using the full conditional,
(w|\cdots)\sim \mathrm{Beta}(\sum_i z_i,\sum_i (1-z_i)).
\item for each $i$, update $z_i$ by Gibbs sampling using the following full conditional,
(z_i|\cdots)\sim\mathrm{B}(1,p_i).
where,
p_i=\frac{w\cdot\mathrm{L_1}(\alpha_u,\beta_u,\alpha_s,\beta_s| n_{ui},n_{si})}{w\cdot\mathrm{L_1}(\alpha_u,\beta_u,\alpha_s,\beta_s|n_{ui},n_{si})+(1-w)\cdot\mathrm{L_0}(\alpha_u,\beta_u|n_{ui},n_{si})}.
For each updated parameter, step 1 above involves the calculation of the following acceptance ratio, (e.g. $\alpha_u$, below),
\begin{split}
\frac{\mathrm{L}(\alpha^{\text{new}}_u,\beta_u,\alpha_s,\beta_s|\cdots)\pi(\alpha^{\text{new}}_u)}{\mathrm{L}(\alpha_u,\beta_u,\alpha_s,\beta_s|\cdots)\pi(\alpha_u)}\\
\end{split}
where $L$ is the complete marginal likelihood conditional on $\mathbf{z}$ defined as,
\mathrm{L}(\alpha_u,\beta_u,\alpha_s,\beta_s|\mathbf{n}_u,\mathbf{n}_s,\mathbf{z})=\prod_i\mathrm{L}_{z_i}(\alpha_u,\beta_u,\alpha_s,\beta_s|\mathbf{n}_u,\mathbf{n}_s)
and $\pi$ is the prior distribution of $\alpha_u$. The obvious changes in the above expression are made for the acceptance ratios of $\alpha_s,\beta_s,\beta_u$. In our case each parameter has the same exponential prior with mean $1,000$

@@

\tilde{Z}(\alpha_u, \beta_u, \alpha_s, \beta_s)=\mathrm{B}(\alpha_u,\beta_u)\mathrm{B}(\alpha_s,\beta_s)\int_{0}^1\frac{{p_u}^{\alpha_u-1}(1-p_u)^{\beta_u-1}}{\mathrm{B}(\alpha_u,\beta_u)}(1-F_{\alpha_s,\beta_s}(p_u))dp_u

@@

\tilde{Z}(\alpha_u, \beta_u, \alpha_s, \beta_s)\approx\mathrm{B}(\alpha_u,\beta_u)\mathrm{B}(\alpha_s,\beta_s)\sum_{k=1}^K(1-F_{\alpha_s,\beta_s}(X_k))

@@

@@

\begin{figure} %  figure placement: here, top, bottom, or page
   \centering
\begin{tikzpicture} [auto,node distance=0cm]
%\node at (0,0) (A) {
%\begin{tikzpicture}
%    \node[anchor=south west,inner sep=0] at (0,0) (a) {\includegraphics[width=0.4\columnwidth]{Figures/Sim_Twosided_ROC_5000.pdf}};
%    \begin{scope} [x={(a.south east)},y={(a.north west)}]
%        \node at (0,1) [font=\small\sffamily] {A} ;
%    \end{scope}
%    \end{tikzpicture}
%    };
%    \node [right=of A] (B) {
%    \begin{tikzpicture}
%    \node[anchor=south west, inner sep=0] at (0,0) (b) {\includegraphics[width=0.4\columnwidth]{Figures/Sim_Twosided_FDR_5000.pdf}};
%        \begin{scope} [x={(b.south east)},y={(b.north west)}]
%        \node at (0,1) [font=\small\sffamily] {B} ;
%        \end{scope}
%    \end{tikzpicture}
%    };
    \node at (0,0) (A) {
    \begin{tikzpicture}
     \node[anchor=south west,inner sep=0] at (0,0) (c) {\includegraphics[width=0.4\columnwidth]{Figures/Sim_Truncated_ROC_5000.pdf}};
         \begin{scope} [x={(c.south east)},y={(c.north west)}]
                 \node at (0,1) [font=\tiny\sffamily] {A} ;
	\end{scope}
     \end{tikzpicture}
     };
     \node [right=of A] (B) {
     \begin{tikzpicture}
    \node[anchor=south west, inner sep=0] at (0,0) (d) {\includegraphics[width=0.4\columnwidth]{Figures/Sim_Truncated_FDR_5000.pdf}};
        \begin{scope} [x={(d.south east)},y={(d.north west)}]
            \node at (0,1) [font=\tiny\sffamily] {B} ;
\end{scope}
    \end{tikzpicture}
    };
  \node [below=of A] (C) {
\begin{tikzpicture}
    \node[anchor=south west,inner sep=0] at (0,0) (e) {\includegraphics[width=0.4\columnwidth]{Figures/Sim_Truncated_ROC_1000.pdf}};
    \begin{scope} [x={(e.south east)},y={(e.north west)}]
        \node at (0,1) [font=\tiny\sffamily] {C} ;
    \end{scope}
    \end{tikzpicture}
    };
    \node [right=of C] (D) {
    \begin{tikzpicture}
    \node[anchor=south west, inner sep=0] at (0,0) (f) {\includegraphics[width=0.4\columnwidth]{Figures/Sim_Truncated_FDR_1000.pdf}};
        \begin{scope} [x={(f.south east)},y={(f.north west)}]
        \node at (0,1) [font=\tiny\sffamily] {D} ;
        \end{scope}
    \end{tikzpicture}
    };
%     \node [below=of C] (E) {
%     \begin{tikzpicture}
%      \node[anchor=south west,inner sep=0] at (0,0) (g) {\includegraphics[width=0.4\columnwidth]{Figures/Sim_Twosided_ROC_1000.pdf}};
%          \begin{scope} [x={(g.south east)},y={(g.north west)}]
%                  \node at (0,1) [font=\tiny\sffamily] {E} ;
% 	\end{scope}
%      \end{tikzpicture}
%      };
%      \node [right=of E] (F) {
%      \begin{tikzpicture}
%     \node[anchor=south west, inner sep=0] at (0,0) (h) {\includegraphics[width=0.4\columnwidth]{Figures/Sim_Twosided_FDR_1000.pdf}};
%         \begin{scope} [x={(h.south east)},y={(h.north west)}]
%             \node at (0,1) [font=\tiny\sffamily] {F} ;
% \end{scope}
%     \end{tikzpicture}
%     };
 \end{tikzpicture}
   \caption{Unconstrained MIMOSA model fit to data from a model
     violating model assumptions and to two-sided data with small
     counts. Data was simulated from a model where proportions were
     sampled from a truncated normal distribution over $[0,1]$ rather
     than a Beta distribution.  A) The average ROC from 10 simulation
     with N=5,000 events. B) The average observed and nominal FDR from
     10 simulations with N=5,000 events. C) Average ROC for N=1,000
     events D) Average observed and nominal FDR for N=1,000 events.
% MIMOSA fit to two-sided data were simulated from the standard model
% with N=1,000 events. E) Average ROC curves from 10 simulations and
% F) average observed vs nominal FDR from 10 simulations. This figure
% appears in color in the electronic version of this article.
}
   \label{webfig:simulations_trunc}
\end{figure}
\bibliographystyle{biom}
\bibliography{MIMOSA}

>>>>

\documentclass{article}
\usepackage[margin=1in]{geometry}
\usepackage{amssymb}
\usepackage{authblk}

\usepackage{booktabs}
\usepackage{multirow,natbib}
\usepackage{url}
\def\bSig\mathbf{\Sigma}
\newcommand{\VS}{V\&S}
\newcommand{\tr}{\mbox{tr}}
\usepackage{amsmath,tikz}
\usetikzlibrary{calc}
\usetikzlibrary{positioning}
\title{Mixture Models for Single-Cell Assays with Application to Vaccine Studies: Supplementary Materials}

 \author{GREG FINAK$^{1\ast}$, 
 ANDREW MCDAVID$^{1}$,
 PRATIP CHATTOPADHYAY$^{3}$,
 MARIA DOMINGUEZ$^{3}$,
 STEVE DE ROSA$^{1,2}$,
 MARIO ROEDERER$^{3}$, 
 RAPHAEL GOTTARDO$^{1}$\\
\textit{ $^{1}$Vaccine and Infectious Disease Division, Fred Hutchinson Cancer Research Center (FHCRC), Seattle, WA\\
 $^{2}$HIV Vaccine Trials Network, Fred Hutchinson Cancer Research Center (FHCRC), Seattle, WA\\
 $^{3}$Vaccine Research Center, NIAID, NIH, 40 Convent Drive, Rm 5509, Bethesda, MD 20892}}
\date{}
\begin{document}
\maketitle
\appendix
%\renewcommand{\thesection}{\Alph{section}}
\renewcommand{\thesubsection}{Appendix \Alph{subsection}:}
%\setcounter{section}{1}
\setcounter{subsection}{0}
%\setcounter{figure}{0}
\renewcommand{\figurename}{\textbf{Supplementary Figure}}
\renewcommand{\thefigure}{\textbf{\arabic{figure}}}
\setcounter{figure}{0}
%\todo[inline]{Note that the Supplementary Information section needs corrections to notation and overall}

\section*{}

@@

\tilde{Z}(\alpha_u, \beta_u, \alpha_s, \beta_s)=\mathrm{B}(\alpha_u,\beta_u)\mathrm{B}(\alpha_s,\beta_s)\int_{0}^1\frac{{p_u}^{\alpha_u-1}(1-p_u)^{\beta_u-1}}{\mathrm{B}(\alpha_u,\beta_u)}[1-F_{\alpha_s,\beta_s}(p_u)]dp_u

@@

\tilde{Z}(\alpha_u, \beta_u, \alpha_s, \beta_s)\approx\mathrm{B}(\alpha_u,\beta_u)\mathrm{B}(\alpha_s,\beta_s)\sum_{k=1}^K[1-F_{\alpha_s,\beta_s}(X_k)]

@@

\subsection{Computational details for the beta-binomial model}
\noindent\textbf{Marginal likelihood derivations}\\
For a given subject $i$, the null marginal likelihood is obtained after integrating out the prior from the likelihood for model ${\cal M}_0$, as follows,
\[
\begin{split}
\mathrm{L_0}(\alpha_u,\beta_u|n_{si},n_{ui}) =&\int_0^1 \mathrm{Pr}(n_{si},n_{ui}|p_u)\pi(p_u|\alpha_u,\beta_u)\mathrm{d}p_u\\
=& \int_0^1Pr(n_s|p_u)Pr(n_u|p_u)\pi(p_u|\alpha_u,\beta_u) \mathrm{d}p_u\\
=&\int_0^1\binom{N_s}{n_s}p_u^{n_s}(1-p_u)^{N_s-n_s}\binom{N_u}{n_u}p_u^{n_u}(1-p_u)^{N_u-n_u}\frac{1}{\mathrm{B}(\alpha_u,\beta_u)}p_u^{\alpha_u-1}(1-p_u)^{\beta_u-1} \mathrm{d}p_u\\
=&\binom{N_s}{n_s}\binom{N_u}{n_u}\frac{1}{\mathrm{B}(\alpha_u,\beta_u)}\int_0^1 p_u^{n_s+n_u+\alpha_u-1}(1-p_u)^{N_s+N_u-n_s-n_u+\beta_u-1} \mathrm{d}p_u\\
=&\binom{N_s}{n_s}\binom{N_u}{n_u}\frac{\mathrm{B}(n_s+n_u+\alpha_u,N_s+N_u-n_s-n_u+\beta_0)}{\mathrm{B}(\alpha_u,\beta_u)}.
\end{split}
\]

\noindent\textbf{MCMC algorithm}\\
In what follows, we use $(x|y)$ to denote the conditional distribution of $x$ given $y$. In particular, we use $(x|\cdots)$ to denote the distribution of $x$ conditional on everything else in the model. Our MCMC algorithms cycles through the following steps:
\begin{enumerate}
\item Update each $\alpha_u, \beta_u, \alpha_s$ and $\beta_s$ by Metropolis-Hastings using a Gaussian symmetric proposal where the variance of the proposal is tuned for each parameter using the approach of~\cite{Gelman:2004tc}.
\item Update $w$ by Gibbs sampling using the full conditional,
\[
(w|\cdots)\sim \mathrm{Beta}(\sum_i z_i,\sum_i (1-z_i)).
\]
\item for each $i$, update $z_i$ by Gibbs sampling using the following full conditional,
\[
(z_i|\cdots)\sim\mathrm{B}(1,p_i).
\]
where,
\[
p_i=\frac{w\cdot\mathrm{L_1}(\alpha_u,\beta_u,\alpha_s,\beta_s| n_{ui},n_{si})}{w\cdot\mathrm{L_1}(\alpha_u,\beta_u,\alpha_s,\beta_s|n_{ui},n_{si})+(1-w)\cdot\mathrm{L_0}(\alpha_u,\beta_u|n_{ui},n_{si})}.
\]
\end{enumerate}
For each updated parameter, step 1 above involves the calculation of the following acceptance ratio, (e.g. $\alpha_u$, below),
\[
\begin{split}
\frac{\mathrm{L}(\alpha^{\text{new}}_u,\beta_u,\alpha_s,\beta_s|\cdots)\pi(\alpha^{\text{new}}_u)}{\mathrm{L}(\alpha_u,\beta_u,\alpha_s,\beta_s|\cdots)\pi(\alpha_u)}\\
\end{split}
\]
where $L$ is the complete marginal likelihood conditional on $\mathbf{z}$ defined as,
\[
\mathrm{L}(\alpha_u,\beta_u,\alpha_s,\beta_s|\mathbf{n}_u,\mathbf{n}_s,\mathbf{z})=\prod_i\mathrm{L}_{z_i}(\alpha_u,\beta_u,\alpha_s,\beta_s|\mathbf{n}_u,\mathbf{n}_s)
\]
and $\pi$ is the prior distribution of $\alpha_u$. The obvious changes in the above expression are made for the acceptance ratios of $\alpha_s,\beta_s,\beta_u$. In our case each parameter has the same exponential prior with mean $1,000$

@@

 \begin{figure}
   \centering
   \begin{tikzpicture} [auto,node distance=0cm]
     \node at (0,0) (A) {
       \begin{tikzpicture}
         \node[anchor=south west,inner sep=0] at (0,0) (c) {\includegraphics[width=0.4\columnwidth]{Figures/post_density_plots.pdf}};
         \begin{scope} [x={(c.south east)},y={(c.north west)}]
           \node at (0,1) [font=\tiny\sffamily] {A} ;
         \end{scope}
       \end{tikzpicture}
      };
    \end{tikzpicture}
    \caption{Histogram of the empirical proportions of unstimulated cells
      and overlaid posterior densities of the beta distribution with
      $\alpha_u$ and $\beta_u$ estimated from the data for ENV-1-PTEG
      stimulated, IFN--$\gamma$+, CD4+ T--cells, demonstrating that the assumption of a common distribution for $p_{iu}$ across subjects is reasonable. }
   \label{fig:empiricalpdist}
 \end{figure}

\begin{figure} %  figure placement: here, top, bottom, or page
   \centering
\begin{tikzpicture} [auto,node distance=0cm]
%\node at (0,0) (A) {
%\begin{tikzpicture}
%    \node[anchor=south west,inner sep=0] at (0,0) (a) {\includegraphics[width=0.4\columnwidth]{Figures/Sim_Twosided_ROC_5000.pdf}};
%    \begin{scope} [x={(a.south east)},y={(a.north west)}]
%        \node at (0,1) [font=\small\sffamily] {A} ;
%    \end{scope}
%    \end{tikzpicture}
%    };
%    \node [right=of A] (B) {
%    \begin{tikzpicture}
%    \node[anchor=south west, inner sep=0] at (0,0) (b) {\includegraphics[width=0.4\columnwidth]{Figures/Sim_Twosided_FDR_5000.pdf}};
%        \begin{scope} [x={(b.south east)},y={(b.north west)}]
%        \node at (0,1) [font=\small\sffamily] {B} ;
%        \end{scope}
%    \end{tikzpicture}
%    };
    \node at (0,0) (A) {
    \begin{tikzpicture}
     \node[anchor=south west,inner sep=0] at (0,0) (c) {\includegraphics[width=0.4\columnwidth]{Figures/Sim_Truncated_ROC_5000.pdf}};
         \begin{scope} [x={(c.south east)},y={(c.north west)}]
                 \node at (0,1) [font=\tiny\sffamily] {A} ;
	\end{scope}
     \end{tikzpicture}
     };
     \node [right=of A] (B) {
     \begin{tikzpicture}
    \node[anchor=south west, inner sep=0] at (0,0) (d) {\includegraphics[width=0.4\columnwidth]{Figures/Sim_Truncated_FDR_5000.pdf}};
        \begin{scope} [x={(d.south east)},y={(d.north west)}]
            \node at (0,1) [font=\tiny\sffamily] {B} ;
\end{scope}
    \end{tikzpicture}
    };
  \node [below=of A] (C) {
\begin{tikzpicture}
    \node[anchor=south west,inner sep=0] at (0,0) (e) {\includegraphics[width=0.4\columnwidth]{Figures/Sim_Truncated_ROC_1000.pdf}};
    \begin{scope} [x={(e.south east)},y={(e.north west)}]
        \node at (0,1) [font=\tiny\sffamily] {C} ;
    \end{scope}
    \end{tikzpicture}
    };
    \node [right=of C] (D) {
    \begin{tikzpicture}
    \node[anchor=south west, inner sep=0] at (0,0) (f) {\includegraphics[width=0.4\columnwidth]{Figures/Sim_Truncated_FDR_1000.pdf}};
        \begin{scope} [x={(f.south east)},y={(f.north west)}]
        \node at (0,1) [font=\tiny\sffamily] {D} ;
        \end{scope}
    \end{tikzpicture}
    };
%     \node [below=of C] (E) {
%     \begin{tikzpicture}
%      \node[anchor=south west,inner sep=0] at (0,0) (g) {\includegraphics[width=0.4\columnwidth]{Figures/Sim_Twosided_ROC_1000.pdf}};
%          \begin{scope} [x={(g.south east)},y={(g.north west)}]
%                  \node at (0,1) [font=\tiny\sffamily] {E} ;
% 	\end{scope}
%      \end{tikzpicture}
%      };
%      \node [right=of E] (F) {
%      \begin{tikzpicture}
%     \node[anchor=south west, inner sep=0] at (0,0) (h) {\includegraphics[width=0.4\columnwidth]{Figures/Sim_Twosided_FDR_1000.pdf}};
%         \begin{scope} [x={(h.south east)},y={(h.north west)}]
%             \node at (0,1) [font=\tiny\sffamily] {F} ;
% \end{scope}
%     \end{tikzpicture}
%     };
 \end{tikzpicture}
   \caption{Unconstrained MIMOSA model fit to data from a model
     violating model assumptions and to two-sided data with small
     counts. Data was simulated from a model where proportions were
     sampled from a truncated normal distribution over $[0,1]$ rather
     than a Beta distribution.  A) The average ROC from 10 simulation
     with N=5,000 events. B) The average observed and nominal FDR from
     10 simulations with N=5,000 events. C) Average ROC for N=1,000
     events D) Average observed and nominal FDR for N=1,000 events.
% MIMOSA fit to two-sided data were simulated from the standard model
% with N=1,000 events. E) Average ROC curves from 10 simulations and
% F) average observed vs nominal FDR from 10 simulations. This figure
% appears in color in the electronic version of this article.
}
   \label{webfig:simulations_trunc}
\end{figure}
\clearpage

\bibliographystyle{biorefs}
\bibliography{MIMOSA}

### 2012-12-03 TIKZFig2.tex
Revised for Biostatistics

\documentclass{article}
\usepackage{tikz,amsmath,siunitx}
\usetikzlibrary{calc}
\usetikzlibrary{positioning}
\usetikzlibrary{arrows,snakes,backgrounds,patterns,matrix,shapes,fit,calc,shadows,plotmarks}
\usepackage[graphics,tightpage,active]{preview}
\PreviewEnvironment{tikzpicture}
\PreviewEnvironment{equation}
\PreviewEnvironment{equation*}
\newlength{\imagewidth}
\newlength{\imagescale}
\pagestyle{empty}
\thispagestyle{empty}
\begin{document}
\begin{tikzpicture} [auto, node distance=0cm]
\node at (0,0) (A){
    \begin{tikzpicture}
    \node[anchor=south west,inner sep=0] at (0,0) (foo) {\includegraphics[width=\columnwidth]{Figures/2.pdf}};
    \begin{scope}[x={(foo.south east)},y={(foo.north west)}]
    \node at (0,1) [font=\tiny\sffamily] {A} ;
    \node at (0.5,1) [font=\tiny\sffamily] {B} ;
    \end{scope}
\end{tikzpicture}
 };
 \node [below=of A] (B) {
 \begin{tikzpicture}
    \node[anchor=south west, inner sep=0] at (0,0) (bar){\includegraphics[width=\columnwidth]{Figures/1.pdf}};
    \begin{scope} [x={(bar.south east)},y={(bar.north west)}]
    \node at (0,1) [font=\tiny\sffamily] {C} ;
    \node at (0.5,1) [font=\tiny\sffamily] {D} ;
    \end{scope}
    \end{tikzpicture}
 };
  \node [below=of B] (E) {
 \begin{tikzpicture}
    \node[anchor=south west, inner sep=0] at (0,0) (baz){\includegraphics[width=\columnwidth]{Figures/15.pdf}};
    \begin{scope} [x={(baz.south east)},y={(baz.north west)}]
    \node at (0,1) [font=\tiny\sffamily] {E} ;
    \node at (0.5,1) [font=\tiny\sffamily] {F} ;
    \end{scope}
    \end{tikzpicture}
 };
\end{tikzpicture}
\end{document}

>>>>

\documentclass{article}
\usepackage{tikz,amsmath,siunitx}
\usetikzlibrary{calc}
\usetikzlibrary{positioning}
\usetikzlibrary{arrows,snakes,backgrounds,patterns,matrix,shapes,fit,calc,shadows,plotmarks}
\usepackage[graphics,tightpage,active]{preview}
\PreviewEnvironment{tikzpicture}
\PreviewEnvironment{equation}
\PreviewEnvironment{equation*}
\newlength{\imagewidth}
\newlength{\imagescale}
\pagestyle{empty}
\thispagestyle{empty}
\begin{document}
\begin{tikzpicture} [auto,node distance=0cm]
\node at (0,0) (A) {
\begin{tikzpicture}
\node[anchor=south west, inner sep=0] at (0,0) (foo) {\includegraphics[width=0.5\columnwidth]{Figures/Fluidigm_plot1.pdf}};
\begin{scope} [x={(foo.south east)},y={(foo.north west)}]
\node at (0,1) [font=\tiny\sffamily] {A} ;
\end{scope}
\end{tikzpicture}
};
\node [right=of A] (B) {
\begin{tikzpicture}
\node[anchor=south west, inner sep=0] at (0,0) (bar) {\includegraphics[width=0.5\columnwidth]{Figures/Fluidigm_plot2.pdf}};
\begin{scope} [x={(bar.south east)},y={(bar.north west)}]
\node at (-0.1,1.1) [font=\tiny\sffamily] {B} ;
\end{scope}
\end{tikzpicture}
};
\node [below=of A] (C) {
\begin{tikzpicture}
\node[anchor=south west, inner sep=0] at (0,0) (baz) {\includegraphics[width=0.5\columnwidth]{Figures/FluidigmFisher.pdf}};
\begin{scope} [x={(baz.south east)},y={(baz.north west)}]
\node at (-0.05,1) [font=\tiny\sffamily] {C} ;
\end{scope}
\end{tikzpicture}
};
\end{tikzpicture}
\end{document}

### 2012-12-03 TIKZFig3.tex
Revised for Biostatistics

\documentclass{article}
\usepackage{tikz,amsmath,siunitx}
\usetikzlibrary{calc}
\usetikzlibrary{positioning}
\usetikzlibrary{arrows,snakes,backgrounds,patterns,matrix,shapes,fit,calc,shadows,plotmarks}
\usepackage[graphics,tightpage,active]{preview}
\PreviewEnvironment{tikzpicture}
\PreviewEnvironment{equation}
\PreviewEnvironment{equation*}
\newlength{\imagewidth}
\newlength{\imagescale}
\pagestyle{empty}
\thispagestyle{empty}
\begin{document}
\begin{tikzpicture} [auto, node distance=0cm]
\node at (0,0) (A){
    \begin{tikzpicture}
    \node[anchor=south west,inner sep=0] at (0,0) (foo) {\includegraphics[width=\columnwidth]{Figures/2.pdf}};
    \begin{scope}[x={(foo.south east)},y={(foo.north west)}]
    \node at (0,1) [font=\tiny\sffamily] {A} ;
    \node at (0.5,1) [font=\tiny\sffamily] {B} ;
    \end{scope}
\end{tikzpicture}
 };
 \node [below=of A] (B) {
 \begin{tikzpicture}
    \node[anchor=south west, inner sep=0] at (0,0) (bar){\includegraphics[width=\columnwidth]{Figures/1.pdf}};
    \begin{scope} [x={(bar.south east)},y={(bar.north west)}]
    \node at (0,1) [font=\tiny\sffamily] {C} ;
    \node at (0.5,1) [font=\tiny\sffamily] {D} ;
    \end{scope}
    \end{tikzpicture}
 };
  \node [below=of B] (E) {
 \begin{tikzpicture}
    \node[anchor=south west, inner sep=0] at (0,0) (baz){\includegraphics[width=\columnwidth]{Figures/15.pdf}};
    \begin{scope} [x={(baz.south east)},y={(baz.north west)}]
    \node at (0,1) [font=\tiny\sffamily] {E} ;
    \node at (0.5,1) [font=\tiny\sffamily] {F} ;
    \end{scope}
    \end{tikzpicture}
 };
\end{tikzpicture}
\end{document}

>>>>

\documentclass{article}
\usepackage{tikz,amsmath,siunitx}
\usetikzlibrary{calc}
\usetikzlibrary{positioning}
\usetikzlibrary{arrows,snakes,backgrounds,patterns,matrix,shapes,fit,calc,shadows,plotmarks}
\usepackage[graphics,tightpage,active]{preview}
\PreviewEnvironment{tikzpicture}
\PreviewEnvironment{equation}
\PreviewEnvironment{equation*}
\newlength{\imagewidth}
\newlength{\imagescale}
\pagestyle{empty}
\thispagestyle{empty}
\begin{document}
  \begin{tikzpicture} [auto, node distance=0cm]
   \node at (0,0) (A) {
\begin{tikzpicture}
    \node [anchor=south west] at (0,0) (foo) {\includegraphics[width=0.5\columnwidth]{Figures/Sim_Onesided_ROC_5000.pdf}};
    \begin{scope}[x={(foo.south east)},y={(foo.north west)}]
        \node at (0,1) [font=\tiny\sffamily] {A} ;
        \end{scope}
    \end{tikzpicture}
    };
    \node [right=of A] (B) {
    \begin{tikzpicture}
    \node [anchor=south west] at (0,0) (bar) {\includegraphics[width=0.5\columnwidth]{Figures/Sim_Onesided_FDR_5000.pdf}};
    \begin{scope}[x={(bar.south east)},y={(bar.north west)}]
    \node at (0,1) [font=\tiny\sffamily] {B} ;
    \end{scope}
    \end{tikzpicture}
    };
        \node [below=of A] (C) {
    \begin{tikzpicture}
    \node [anchor=south west] at (0,0) (c) {\includegraphics[width=0.5\columnwidth]{Figures/Sim_Twosided_ROC_5000.pdf}};
    \begin{scope}[x={(c.south east)},y={(c.north west)}]
    \node at (0,1) [font=\tiny\sffamily] {C} ;
    \end{scope}
    \end{tikzpicture}
    };
    \node [right=of C] (D) {
    \begin{tikzpicture}
    \node [anchor=south west] at (0,0) (d) {\includegraphics[width=0.5\columnwidth]{Figures/Sim_Twosided_FDR_5000.pdf}};
    \begin{scope}[x={(d.south east)},y={(d.north west)}]
    \node at (0,1) [font=\tiny\sffamily] {D} ;
    \end{scope}
    \end{tikzpicture}
    };

\end{tikzpicture}
\end{document}

### 2012-12-03 TIKZFig4.tex
Revised for Biostatistics

\documentclass{article}
\usepackage{tikz,amsmath,siunitx}
\usetikzlibrary{calc}
\usetikzlibrary{positioning}
\usetikzlibrary{arrows,snakes,backgrounds,patterns,matrix,shapes,fit,calc,shadows,plotmarks}
\usepackage[graphics,tightpage,active]{preview}
\PreviewEnvironment{tikzpicture}
\PreviewEnvironment{equation}
\PreviewEnvironment{equation*}
\newlength{\imagewidth}
\newlength{\imagescale}
\pagestyle{empty}
\thispagestyle{empty}
\begin{document}
\begin{tikzpicture} [auto,node distance=0cm]
\node at (0,0) (A) {
\begin{tikzpicture}
\node[anchor=south west, inner sep=0] at (0,0) (foo) {\includegraphics[width=0.5\columnwidth]{Figures/Fluidigm_plot1.pdf}};
\begin{scope} [x={(foo.south east)},y={(foo.north west)}]
\node at (0,1) [font=\tiny\sffamily] {A} ;
\end{scope}
\end{tikzpicture}
};
\node [right=of A] (B) {
\begin{tikzpicture}
\node[anchor=south west, inner sep=0] at (0,0) (bar) {\includegraphics[width=0.5\columnwidth]{Figures/Fluidigm_plot2.pdf}};
\begin{scope} [x={(bar.south east)},y={(bar.north west)}]
\node at (-0.1,1.1) [font=\tiny\sffamily] {B} ;
\end{scope}
\end{tikzpicture}
};
\node [below=of A] (C) {
\begin{tikzpicture}
\node[anchor=south west, inner sep=0] at (0,0) (baz) {\includegraphics[width=0.5\columnwidth]{Figures/FluidigmFisher.pdf}};
\begin{scope} [x={(baz.south east)},y={(baz.north west)}]
\node at (-0.05,1) [font=\tiny\sffamily] {C} ;
\end{scope}
\end{tikzpicture}
};
\end{tikzpicture}
\end{document}

>>>>

\documentclass{article}
\usepackage{tikz,amsmath,siunitx}
\usetikzlibrary{calc}
\usetikzlibrary{positioning}
\usetikzlibrary{arrows,snakes,backgrounds,patterns,matrix,shapes,fit,calc,shadows,plotmarks}
\usepackage[graphics,tightpage,active]{preview}
\PreviewEnvironment{tikzpicture}
\PreviewEnvironment{equation}
\PreviewEnvironment{equation*}
\newlength{\imagewidth}
\newlength{\imagescale}
\pagestyle{empty}
\thispagestyle{empty}
\begin{document}
\begin{tikzpicture} [auto, node distance=0 cm]
\node at (0,0) (A) {
\begin{tikzpicture}
\node[anchor=south west, inner sep=0] at (0,0) (foo) {\includegraphics[width=0.5\columnwidth]{Figures/Fluidigm_Multivariate_BIRC3_CCL5_Unstim_Counts.pdf}};
\begin{scope} [x={(foo.south east)},y={(foo.north west)}]
\node at (0,1) [font=\tiny\sffamily] {A} ;
\end{scope}
\end{tikzpicture}
};
\node [right=of A] (B){
\begin{tikzpicture}
\node[anchor=south west, inner sep=0] at (0,0) (bar) {\includegraphics[width=0.5\columnwidth]{Figures/Fluidigm_Multivariate_BIRC3_CCL5_Stim_Counts.pdf}};
\begin{scope} [x={(bar.south east)},y={(bar.north west)}]
\node at (-0.02,1) [font=\tiny\sffamily] {B} ;
\end{scope}
\end{tikzpicture}
};
%\node [anchor = south west, inner sep=0] at (0,-4) {\includegraphics[width=0.4\columnwidth]{Fluidigm_Multivariate_Marginalized_BIRC3_CCL5.pdf}};
%\node [anchor=south west, inner sep=0] at (6.5,-4) {\includegraphics[width=0.4\columnwidth]{Fluidigm_Multivariate_BIRC3_CCL5.pdf}};
%\node at (0,0) [font=\small\sffamily] {C} ;
%\node at (6.25,0) [font=\small\sffamily] {D} ;
\end{tikzpicture}\end{document}
